% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=[rgb]{0, 0.1,0.5},    
    urlcolor=[rgb]{0,0.1,0.5},
}


\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
\headerrow
	{\LARGE \textbf{Francisco Javier Ponce Cruz}}
	{\href{https://github.com/fjavierponce}{github.com/fjavierponce}}
\\
\headerrow
	{fco.poncecruz@gmail.com \textbullet \ \ (+52) 55 23 44 41 96}
	{Java,  \CPP, Python}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	%%% SKYTOUCH %%%
	\item
	\headerrow
		{\textbf{SkyTouch Technology}}
		{\textbf{Mexico City}}
	\\
	\headerrow
		{\emph{Software Engineer}}
		{\emph{October 2018 – Present}}
	\begin{itemize*}
		\item Contributed to sign a new deal for approximately \$70k by developing the interface of TravelClick iHotelier.
		\item Helped +1,110 hotels to generate simple receipts for both guests, and non-room guests for sundry purchases, 
		by developing the QuickShop project for the Hotel OS in \textbf{Java}.
		\item Improved the onboarding process by documenting, mentoring and encouraging team members to mentor new candidates for 
		Software Engineer positions. 
	\end{itemize*}

	%%% Lending Club %%%
	\item
	\headerrow
		{\textbf{Lending Club}}
		{\textbf{Mexico City}}
	\\
	\headerrow
		{\emph{Java Developer}}
		{\emph{December 2017 – October 2018}}
	\begin{itemize*}
		\item Integrated the Borrower mobile application with the backend services, by developing the API Gateway and migrating
		 to microservices architecture.
		\item Developed the RESTful API for Investor project using \textbf{Java}.
	\end{itemize*}

	%%% Tom Sawyer %%%
	\item
	\headerrow
		{\textbf{Tom Sawyer Software}}
		{\textbf{Mexico City}}
	\\
	\headerrow
		{\emph{Product Development Engineer}}
		{\emph{July 2016 – December 2017}}
	\begin{itemize*}
		\item Decreased startup time of the data visualization product by 40\%, by creating a new classpath scanning mechanism 
		using \textbf{Java and Spring}.
		\item Redesigned the build system and DevOps infrastructure, by migrating the Ant-based build to Maven.
		\item Contributed to the strategic upgrade of Tom Sawyer Perspectives 8.0, by assembling the Systems Engineering and 
		Business Process modules into one Data visualization product.
	\end{itemize*}
	
	%%% Legosoft %%%
	\item
	\headerrow
		{\textbf{LegoSoft}}
		{\textbf{Mexico City}}
	\\
	\headerrow
		{\emph{Java Liferay Developer}}
		{\emph{May 2015 – June 2016}}
	\begin{itemize*}
		\item Consolidated the use of Vaadin and Liferay in the company, by executing technical proposal presentations for potential clients, 
		and mentoring team members in these technologies.
		\item Led the development of a social portal using Liferay and Vaadin, in a team of 3 developers and 2 analysts.
		\item Developed the CRM system for the project UNIFIN insurance company, in a team of 3 developers.
	\end{itemize*}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em
	
	%%% ESCOM %%%
	\item 
	\headerrow
    		{\textbf{Instituto Polit\'ecnico Nacional}}
		{\textbf{Mexico City}}
	\\
	\headerrow
		{\emph{B.E. Computer Systems Engineering (Grade 8.78 / 10)}}
		{\emph{August 2010 - February 2015}}
	\begin{itemize*}
		\item Thesis: A Software Testing methodology based on Functionality and Performance Metrics.
	\end{itemize*}

	%%% CTU %%%
	\item 
	\headerrow
    		{\textbf{Czech Technical University in Prague}}
		{\textbf{Czech Republic}}
	\\
	\headerrow
		{\emph{International Exchange Program}}
		{\emph{January 2013 - July 2013}}
	\begin{itemize*}
		\item Attended Web 2.0, Latex, Node.js, Signals and Systems and Economics, as Exchange Student in the Faculty of Information Technology.
	\end{itemize*}

	%%% Batiz %%%
	\item 
	\headerrow
    		{\textbf{Instituto Politécnico Nacional CECyT 9}}
		{\textbf{Mexico City}}
	\\
	\headerrow
		{\emph{Computer Technician}}
		{\emph{January 2013 - July 2013}}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% Leadership and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Leadership and Awards}

\begin{itemize}
	\parskip=0.1em
	
	%%% CTU %%%
	\item 
	\headerrow
    		{\textbf{International Exchange Program}}
		{\emph{January 2013 - July 2013}}	
	\begin{itemize*}
		\item I was awarded a scholarship among the 10 best students over approximately 250 at my University to study abroad, at the 
		Faculty of Information Technology FIT-CTU in Prague.
	\end{itemize*}
	
	%%% ESCOM Exchange group %%%
	\item 
	\headerrow
    		{\textbf{Exchange Students Group}}
		{\emph{August 2015 – December 2015}}
	\begin{itemize*}
		\item Member of the Exchange Students Group at my university, helping students through the process to pursue a scholarship to study abroad, 
		and giving talks about my experience in the Czech Republic.
	\end{itemize*}
	
	%%% Oratoria %%%
	\item 
	\headerrow
    		{\textbf{Course: “Oratory, the art of public speaking” }}
		{\emph{January 2014 – March 2014}}
	\begin{itemize*}
		\item Attended classes of Public speaking, speech planning, and body language techniques.
	\end{itemize*}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item -- \textbf{Languages:} Java, Clojure, C, \CPP, \LaTeX, Python, Shell Script, SQL, TypeScript.
	\item -- \textbf{Technical skills and frameworks:} Git, JUnit, AssertJ, Spring, Docker, RabbitMQ, Maven, TypeScript, 
	Jenkins, Vaadin, Liferay, Agile (Scrum, Kanban).
\end{description*}
\end{indentsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% Other Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Interests and Other Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item -- \textbf{Spanish}, mother tongue. Fluent in \textbf{English} (TOEFL iBT 87). Basic \textbf{French} proficiency (A2 CEFR).
	\item -- Inclined to never say I can't.
	\item -- Self-motivated and passionate about learning and growing intellectually. Always searching for challenges.
	\item -- Interested in Mathematics, Algorithms, Quantum Computing, Geostrategy and Aviation.
\end{description*}
\end{indentsection}

\end{document}
